Optimal Sizing of Stand-alone Solar PV Systems Through Automated Formal Synthesis Method

### 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Just to compare the results obtained from the optimization 
with the real-world, the authors had four PV systems deployed 
and monitored since June $2018$ in a riverside community 
in the Amazonas State in Brazil (coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W), with similar power demands 
presented by case studies $1$, $4$, $5$, and $6$, 
always with a $3$ $\times$ $325$ W ($3$S) panels and 
$4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) 
lead-acid batteries. These solutions are more close 
to the result presented by our formal synthesis 
approach than HOMER Pro, thereby showing that our 
solution is sound, which answers \textit{EQ1}.

Related to the inverters, HOMER Pro suggests a value in 
kW very close to the peak of every case study, and it 
is just a reference value and not a commercial value of 
the employed inverter. Our synthesis tool, however, 
presents inverters that are commercial and can be found 
off-the-shelf. Therefore is a PRO to the formal synthesis method.

Concerning to charge controllers, as we reported in 
the previous section, HOMER Pro does not include it 
as an explicit equipment in its mathematical model, 
only our synthesis tool presents a commercial controller 
and includes it during the cost analysis. Therefore, 
the formal synthesis method presents more reliable results than
HOME Pro.

Case study $7$ was not solved by our synthesis tool 
within the time limit established during the experimental 
phase. Case study $3$ was not possible to simulate in HOMER Pro, 
because its restriction does not allow one to set the battery autonomy, 
thus resting both without parameters to comparative.

>>>>

To compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil (coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W), with similar power demands presented by case studies $1$, $4$, $5$, and $6$, 
always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries. These solutions are closer to the result presented by our formal synthesis approach than HOMER Pro, thereby showing that our solution is sound, which answers \textit{EQ1}.

Related to the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter. Our synthesis tool, however, 
presents inverters that are commercial and can be found off-the-shelf; therefore, our approach is a PRO to the formal synthesis method.

Concerning the charge controllers, as we reported in the previous section, HOMER Pro does not include it as an explicit equipment in its mathematical model; only our synthesis tool presents a commercial controller and includes it during the cost analysis. Therefore, the formal synthesis method presents more reliable results than HOME Pro.

Our synthesis tool did not solve the case study $7$  within the time limit established during the experimental phase. Case study $3$ was not possible to simulate in HOMER Pro, because its restriction does not allow one to set the battery autonomy, thus resting both without parameters for comparison.
